Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-20 ms.tex
Updated constraints in table, updated triangle figure with latest runs, small edits.

$-21$ & Zentner+16 & $12.92^{+0.07}_{-0.11}$ & $0.74^{+0.09}_{-0.16}$ & $13.93^{+0.04}_{-0.05}$ & $1.23^{+0.10}_{-0.12}$ & $--$ & $--$ & 1.59\\

@@

$-20$ & Zentner+16 & $11.95^{+0.11}_{-0.6}$ & $0.37^{+0.23}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.19\\
$-20$ & Zentner+16 & $12.23^{+0.33}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.20^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.32}_{-0.26}$ & 1.16 \vspace*{5pt}\\

@@

$-19$ & Zentner+16 & $11.72^{+0.33}_{-0.19}$ & $0.69^{+0.52}_{-0.46}$ & $12.78^{+0.04}_{-0.04}$ & $1.03^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.77\\

@@

The one-dimensional marginalized constraints on all parameters from
these analyses are given in the lowest row of each luminosity
threshold grouping in Table~\ref{table:parameters}.  In cases where
the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ is
a monotonic within the physical parameter range, we quote an upper or
lower limit on the parameter (e.g., see the posterior distribution for
$A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}).  Examples of one- and
two-dimensional visualizations of the posteriors from our analyses are
shown in Figure~\ref{fig:Mr19ABtriangle},
Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}
for the $M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.

@@

This ``splashback" hypothesis has further merit in that it has the
same sense as suggested by the data. Splashback halos have experienced
mass loss as a consequence of their tidal interactions with a larger,
nearby halo. As a consequence, splashback halos are expected to be
less massive than `regular' host halos that host similar galaxies
\citep{dalal_etal08}.  Meanwhile, high concentrations due to tidal
truncation are a hallmark of splashback halos
\citep{wang_etal07,dalal_etal08,sunayama_etal16}.  The implication is
a population of halos, correlated on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, that have concentrations that are high for their
mass and galaxies that are overluminous for their mass. This is
precisely the sense of assembly bias suggested by our analysis.  Note,
though, that this splashback effect cannot explain galaxy assembly
bias on large, linear scales.

>>>>

$-21$ & Zentner+16 & $12.92^{+0.08}_{-0.10}$ & $0.72^{+0.09}_{-0.14}$ & $13.95^{+0.03}_{-0.05}$ & $1.26^{+0.08}_{-0.11}$ & $--$ & $--$ & 1.59\\

@@

$-20$ & Zentner+16 & $11.96^{+0.11}_{-0.06}$ & $0.38^{+0.22}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.88\\
$-20$ & Zentner+16 & $12.24^{+0.29}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.19^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.35}_{-0.27}$ & 1.09 \vspace*{5pt}\\

@@

$-19$ & Zentner+16 & $11.72^{+0.33}_{-0.19}$ & $0.70^{+0.51}_{-0.45}$ & $12.78^{+0.04}_{-0.04}$ & $1.03^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.67\\

@@

The one-dimensional marginalized constraints on all parameters from
these analyses are given in the lowest row of each luminosity
threshold grouping in Table~\ref{table:parameters}.  In cases where
the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ contains significant 
probability at the limits of the parameter range (e.g., see the posterior distribution for
$A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}), we quote one-sided 
constraints.  Examples of one- and
two-dimensional visualizations of the posteriors from our analyses are
shown in Figure~\ref{fig:Mr19ABtriangle},
Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}
for the $M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.

@@

This ``splashback" hypothesis has further merit in that it has the
same sense as suggested by the data. Splashback halos have experienced
mass loss as a consequence of their tidal interactions with a larger,
nearby halo. As a consequence, splashback halos are expected to be
less massive than `regular' host halos that host similar galaxies
\citep{dalal_etal08}.  Meanwhile, high concentrations due to tidal
truncation are a hallmark of splashback halos
\citep{sunayama_etal16}.  The implication is
a population of halos, correlated on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, that have concentrations that are high for their
mass and galaxies that are overluminous for their mass. This is
precisely the sense of assembly bias suggested by our analysis.  Note,
though, that this splashback effect cannot explain galaxy assembly
bias on large, linear scales.
